---
title: "Distributions in R"
author: "Shuhan Song"
date: "2022-12-27"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE, 
                      warning = FALSE)
library(tidyverse)
library(patchwork)
```

## Set Up Distribution Simulations

```{r}
distribution_fcn_ls = c(rbeta=rbeta, rbinom=rbinom, rcauchy=rcauchy, rchisq=rchisq, rexp=rexp, rf=rf, rgamma=rgamma, rgeom=rgeom, rhyper=rhyper, rlnorm=rlnorm, rlogis=rlogis, rnbinom=rnbinom, rnorm=rnorm, rpois=rpois, rsignrank=rsignrank, rt=rt, runif=runif, rweibull=rweibull, rwilcox=rwilcox)

distribution_fcn_name = names(distribution_fcn_ls)

distribution_name = c("Beta", "Binomial", "Cauchy", "Chi-squared", "Exponential", "F", "Gamma", "Geometric", "Hypergeometric", "Lognormal", "Logistic", "Negative binomial", "Normal", "Poisson", "Wilcoxon signed rank", "t", "Uniform", "Weibull", "Wilcoxon rank sum")

n = 10000

sim_fcn = function(fcn, dist_name, bw = 0.01, ...){
  set.seed(123)
  
  df = data.frame(x = fcn(n = n, ...))
  
  p1 = ggplot(df, 
         aes(x = x)) +
       geom_histogram(binwidth = bw, 
                      color = "grey40",
                      fill = "white") +
       theme_bw() +
       labs(title = paste(str_to_title(dist_name), "Distribution")) 
  
  p2 = ggplot(df, 
         aes(x = x)) +
       geom_density(color = "red")+
       theme_bw() +
       labs(title = paste(str_to_title(dist_name), "Distribution")) 
  
  p1+p2
  
}
```


## `r paste(str_to_title(distribution_name[1]), "Distribution", paste0(distribution_fcn_name[1],"()"))`

```{r}
args(distribution_fcn_ls$rbeta)
```


```{r}
distribution_fcn_ls$rbeta %>% 
  sim_fcn(dist_name = distribution_name[1], 
          bw = 0.01,
          # distribution parameters ---
          shape1 = 5, shape2 = 100 # non-negative parameters of Beta distribution
          )
```


```{r}
distribution_fcn_ls$rbeta %>% 
  sim_fcn(dist_name = distribution_name[1], 
          bw = 0.02,
          # distribution parameters ---
          shape1 = 50, shape2 = 5 # non-negative parameters of Beta distribution
          )
```


## `r paste(str_to_title(distribution_name[2]), "Distribution", paste0(distribution_fcn_name[2],"()"))`

```{r}
args(distribution_fcn_ls$rbinom)
```

```{r}
distribution_fcn_ls$rbinom %>% 
  sim_fcn(dist_name = distribution_name[2], 
          bw = 5,
          # distribution parameters ---
          size = 1000, # number of trails
          prob = 0.25 # probability of success on each trail
          )
```



## `r paste(str_to_title(distribution_name[3]), "Distribution", paste0(distribution_fcn_name[3],"()"))`


```{r}
args(distribution_fcn_ls$rcauchy)
```

```{r}
distribution_fcn_ls$rcauchy %>% 
  sim_fcn(dist_name = distribution_name[3], 
          bw = 5,
          # distribution parameters ---
          location = 0, # number of trails
          scale = 1 # probability of success on each trail
          )
```



```{r}
distribution_fcn_ls$rcauchy %>% 
  sim_fcn(dist_name = distribution_name[3], 
          bw = 0.1,
          # distribution parameters ---
          location = 0, # number of trails
          scale = 0.01 # probability of success on each trail
          )
```



```{r}
distribution_fcn_ls$rcauchy %>% 
  sim_fcn(dist_name = distribution_name[3], 
          bw = 0.01,
          # distribution parameters ---
          location = 20, # number of trails
          scale = 0.01 # probability of success on each trail
          )
```




## `r paste(str_to_title(distribution_name[4]), "Distribution", paste0(distribution_fcn_name[4],"()"))`

```{r}
args(distribution_fcn_ls$rchisq)
```

```{r}
distribution_fcn_ls$rchisq %>% 
  sim_fcn(dist_name = distribution_name[4], 
          bw = 5,
          # distribution parameters ---
          df = 100, # degree of freedom
          ncp = 0 # non-centrality parameter
          )
```

```{r}
distribution_fcn_ls$rchisq %>% 
  sim_fcn(dist_name = distribution_name[4], 
          bw = 5,
          # distribution parameters ---
          df = 100, # degree of freedom
          ncp = 20 # non-centrality parameter (non-negative)
          )
```





