---
title: "Distributions in R"
author: "Shuhan Song"
date: "2022-12-27"
output:
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE, 
                      warning = FALSE)
library(tidyverse)
library(patchwork)
```

```{r}
## Set Up Distribution Simulations
distribution_fcn_ls = c(rbeta=rbeta, rbinom=rbinom, rcauchy=rcauchy, 
                        rchisq=rchisq, rexp=rexp, rf=rf, rgamma=rgamma, 
                        rgeom=rgeom, rhyper=rhyper, rlnorm=rlnorm, rlogis=rlogis, 
                        rnbinom=rnbinom, rnorm=rnorm, rpois=rpois, 
                        rsignrank=rsignrank, rt=rt, runif=runif, rweibull=rweibull, 
                        rwilcox=rwilcox)

distribution_fcn_name = names(distribution_fcn_ls)

distribution_name = c("Beta", "Binomial", "Cauchy", "Chi-squared", "Exponential", 
                      "F", "Gamma", "Geometric", "Hypergeometric", "Lognormal", 
                      "Logistic", "Negative binomial", "Normal", "Poisson", 
                      "Wilcoxon signed rank", "t", "Uniform", "Weibull", 
                      "Wilcoxon rank sum")

n = 10000

sim_fcn = function(fcn, dist_name, bw = 0.01, plot_text="", x_lim = NULL, ...){
  set.seed(123)
  
  df = data.frame(x = fcn(n, ...))
  
  p1 = ggplot(df, 
         aes(x = x)) +
       geom_histogram(binwidth = bw, 
                      color = "grey40",
                      fill = "white") +
       theme_bw() +
       labs(title = paste(str_to_title(dist_name), "Distribution")) 
  
  p2 = ggplot(df, 
         aes(x = x)) +
       geom_density(color = "red")+
       theme_bw() +
       labs(caption = plot_text) 
  
  if(is.null(x_lim)){
    p1+p2
  } else {
    ( p1 + xlim(x_lim) ) + ( p2 + xlim(x_lim) )
  }
  
}


sim_ylim_fcn = function(fcn, dist_name, bw = 0.01, plot_text="", x_lim = NULL, y_lim1, y_lim2, ...){
  set.seed(123)
  
  df = data.frame(x = fcn(n, ...))
  
  p1 = ggplot(df, 
         aes(x = x)) +
       geom_histogram(binwidth = bw, 
                      color = "grey40",
                      fill = "white") +
       theme_bw() +
       labs(title = paste(str_to_title(dist_name), "Distribution"))  +
       ylim(y_lim1)
  
  p2 = ggplot(df, 
         aes(x = x)) +
       geom_density(color = "red")+
       theme_bw() +
       labs(caption = plot_text) +
       ylim(y_lim2)
  
  if(is.null(x_lim)){
    p1+p2
  } else {
    ( p1 + xlim(x_lim) ) + ( p2 + xlim(x_lim) )
  }
  
}
```


## `r paste(str_to_title(distribution_name[1]), "Distribution", paste0(distribution_fcn_name[1],"()"))`

```{r echo=TRUE}
args(rbeta)
```


```{r}
plot1 = distribution_fcn_ls$rbeta %>% 
  sim_fcn(dist_name = distribution_name[1], 
          bw = 0.02,
          plot_text = "rbeta(n, shape1 = 5, shape2 = 100)",
          x_lim = c(0,1),
          # distribution parameters ---
          shape1 = 5, shape2 = 100 # non-negative parameters of Beta distribution
          )

plot2 = distribution_fcn_ls$rbeta %>% 
  sim_fcn(dist_name = distribution_name[1], 
          bw = 0.02,
          plot_text = "rbeta(n, shape1 = 20, shape2 = 20)",
          x_lim = c(0,1),
          # distribution parameters ---
          shape1 = 20, shape2 = 20 # non-negative parameters of Beta distribution
          )


plot3 = distribution_fcn_ls$rbeta %>% 
  sim_fcn(dist_name = distribution_name[1], 
          bw = 0.02,
          plot_text = "rbeta(n, shape1 = 50, shape2 = 5)",
          x_lim = c(0,1),
          # distribution parameters ---
          shape1 = 50, shape2 = 5 # non-negative parameters of Beta distribution
          )

plot1 /
plot2 /
plot3
```


## `r paste(str_to_title(distribution_name[2]), "Distribution", paste0(distribution_fcn_name[2],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rbinom)
```

size: number of trails

prob: probability of success on each trail

```{r}
distribution_fcn_ls$rbinom %>% 
  sim_fcn(dist_name = distribution_name[2], 
          bw = 5,
          plot_text = "rbinom(n, size = 1000, prob = 0.25)",
          # distribution parameters ---
          size = 1000, # number of trails
          prob = 0.25 # probability of success on each trail
          )
```



## `r paste(str_to_title(distribution_name[3]), "Distribution", paste0(distribution_fcn_name[3],"()"))`


```{r echo=TRUE}
args(distribution_fcn_ls$rcauchy)
```


```{r echo=FALSE}
plot1 = distribution_fcn_ls$rcauchy %>% 
  sim_fcn(dist_name = distribution_name[3], 
          bw = 0.5,
          plot_text = "rcauchy(n, location = 0, scale = 1)",
          x_lim = c(-10, 10),
          # distribution parameters ---
          location = 0, 
          scale = 1 
          )

plot2 = distribution_fcn_ls$rcauchy %>% 
  sim_fcn(dist_name = distribution_name[3], 
          bw = 0.2,
          plot_text = "rcauchy(n, location = 0, scale = 0.1)",
          x_lim = c(-10, 10),
          # distribution parameters ---
          location = 0, 
          scale = 0.1 
          )

plot3 = distribution_fcn_ls$rcauchy %>% 
  sim_fcn(dist_name = distribution_name[3], 
          bw = 0.2,
          plot_text = "rcauchy(n, location = 5, scale = 0.1)",
          x_lim = c(-10, 10),
          # distribution parameters ---
          location = 5, 
          scale = 0.1
          )

plot1 / # location = 0, scale = 1
  plot2 / # location = 0, scale = 0.01
    plot3  # location = 20, scale = 0.01
```




## `r paste(str_to_title(distribution_name[4]), "Distribution", paste0(distribution_fcn_name[4],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rchisq)
```

df: degree of freedom

ncp: non-centrality parameter (non-negative)

```{r}
plot1 = distribution_fcn_ls$rchisq %>% 
  sim_fcn(dist_name = distribution_name[4], 
          bw = 5,
          plot_text = "rchisq(n, df = 100, ncp = 0)",
          x_lim = c(50,200),
          # distribution parameters ---
          df = 100, # degree of freedom
          ncp = 0 # non-centrality parameter
          )

plot2 = distribution_fcn_ls$rchisq %>% 
  sim_fcn(dist_name = distribution_name[4], 
          bw = 5,
          plot_text = "rchisq(n, df = 100, ncp = 20)",
          x_lim = c(50,200),
          # distribution parameters ---
          df = 100, # degree of freedom
          ncp = 20 # non-centrality parameter (non-negative)
          )

plot1/plot2
```



## `r paste(str_to_title(distribution_name[5]), "Distribution", paste0(distribution_fcn_name[5],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rexp)
```

rate: vector of rates

```{r}
plot1 = distribution_fcn_ls$rexp %>% 
  sim_fcn(dist_name = distribution_name[5], 
          bw = 0.2,
          plot_text = "rexp(n, rate = 1)",
          x_lim = c(0,8),
          # distribution parameters ---
          rate = 1
          )

plot2 = distribution_fcn_ls$rexp %>% 
  sim_fcn(dist_name = distribution_name[5], 
          bw = 0.2,
          plot_text = "rexp(n, rate = 2)",
          x_lim = c(0,8),
          # distribution parameters ---
          rate = 2
          )

plot1/plot2
```


## `r paste(str_to_title(distribution_name[6]), "Distribution", paste0(distribution_fcn_name[6],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rf)
```

df1, df2: degrees of freedom. Inf is allowed.

ncp: non-centrality parameter. If omitted the central F is assumed.


```{r}
plot1 = distribution_fcn_ls$rf %>% 
  sim_fcn(dist_name = distribution_name[6], 
          bw = 0.1,
          plot_text = "rf(n, df1 = 10, df2 = 100, ncp = 0)",
          x_lim = c(0, 4),
          # distribution parameters ---
          df1 = 10, df2 = 100, ncp = 0
          )

plot2 = distribution_fcn_ls$rf %>% 
  sim_fcn(dist_name = distribution_name[6], 
          bw = 0.1,
          plot_text = "rf(n, df1 = 100, df2 = 100, ncp = 0)",
          x_lim = c(0, 4),
          # distribution parameters ---
          df1 = 100, df2 = 100, ncp = 0
          )

plot3 = distribution_fcn_ls$rf %>% 
  sim_fcn(dist_name = distribution_name[6], 
          bw = 0.1,
          plot_text = "rf(n, df1 = 100, df2 = 10, ncp = 0)",
          x_lim = c(0, 4),
          # distribution parameters ---
          df1 = 100, df2 = 10, ncp = 0
          )

plot4 = distribution_fcn_ls$rf %>% 
  sim_fcn(dist_name = distribution_name[6], 
          bw = 0.1,
          plot_text = "rf(n, df1 = 10000, df2 = 10, ncp = 0)",
          x_lim = c(0, 4),
          # distribution parameters ---
          df1 = 10000, df2 = 10, ncp = 0
          )

plot5 = distribution_fcn_ls$rf %>% 
  sim_fcn(dist_name = distribution_name[6], 
          bw = 0.1,
          plot_text = "rf(n, df1 = 10, df2 = 100, ncp = 5)",
          x_lim = c(0, 4),
          # distribution parameters ---
          df1 = 10, df2 = 100, ncp = 5
          )

plot6 = distribution_fcn_ls$rf %>% 
  sim_fcn(dist_name = distribution_name[6], 
          bw = 0.1,
          plot_text = "rf(n, df1 = 10, df2 = 100)",
          # x_lim = c(0, 4),
          # distribution parameters ---
          df1 = 10, df2 = 100
          )

plot1 / plot2 / plot3

plot1 / plot6 / plot5
```


kk## `r paste(str_to_title(distribution_name[7]), "Distribution", paste0(distribution_fcn_name[7],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rgamma)
```

shape, scale: shape and scale parameters. Must be positive, `scale` strictly. 

rate: an alternative way specify the scale

```{r}
plot1 = distribution_fcn_ls$rgamma %>% 
  sim_fcn(dist_name = distribution_name[7],
          bw = 1,
          plot_text = "rgamma(n, shape = 5, rate = 1, scale = 1/rate)",
          x_lim = c(0, 30),
          # distribution parameters ---
          shape = 5
          )

plot2 = distribution_fcn_ls$rgamma %>% 
  sim_fcn(dist_name = distribution_name[7],
          bw = 1,
          plot_text = "rgamma(n, shape = 15, rate = 1, scale = 1/rate)",
          # x_lim = c(0, 30),
          # distribution parameters ---
          shape = 15
          )

plot3 = distribution_fcn_ls$rgamma %>% 
  sim_fcn(dist_name = distribution_name[7],
          bw = 1,
          plot_text = "rgamma(n, shape = 5, rate = 1/3, scale = 1/rate)",
          x_lim = c(0, 30),
          # distribution parameters ---
          shape = 5, rate = 1/3
          )

plot1 / plot2 / plot3
```


## `r paste(str_to_title(distribution_name[8]), "Distribution", paste0(distribution_fcn_name[8],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rgeom)
```

prob: probability of success in each trial. 0 < prob <= 1.

```{r}
plot1 = distribution_fcn_ls$rgeom %>% 
  sim_ylim_fcn(dist_name = distribution_name[8],
          bw = 0.2,
          plot_text = "rgeom(n, prob = 0.3)",
          x_lim = c(0, 10),
          y_lim1 = c(0, 3000),
          y_lim2 = c(0, 3),
          # distribution parameters ---
          prob = 0.3
          )

plot2 = distribution_fcn_ls$rgeom %>% 
  sim_ylim_fcn(dist_name = distribution_name[8],
          bw = 0.2,
          plot_text = "rgeom(n, prob = 0.5)",
          x_lim = c(0, 10),
          y_lim1 = c(0, 3000),
          y_lim2 = c(0, 3),
          # distribution parameters ---
          prob = 0.5
          )

plot3 = distribution_fcn_ls$rgeom %>% 
  sim_ylim_fcn(dist_name = distribution_name[8],
          bw = 0.1,
          plot_text = "rgeom(n, prob = 0.7)",
          x_lim = c(0, 10),
          y_lim1 = c(0, 3000),
          y_lim2 = c(0, 3),
          # distribution parameters ---
          prob = 0.7
          )

plot1/plot2/plot3
```


## `r paste(str_to_title(distribution_name[9]), "Distribution", paste0(distribution_fcn_name[9],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rhyper)
```

m: the number of white balls in the urn

n: the number of black balls in the urn

k: the number of balls drawn from the urn. 0 <= k <= m+n


1. changing k

```{r}
plot1 = distribution_fcn_ls$rhyper %>% 
  sim_ylim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 10, n = 10, k = 1)",
          x_lim = c(-0.5, 10.5),
          y_lim1 = c(0,10000),
          y_lim2 = c(0,3),
          # distribution parameters ---
          m = 10, n = 10, k = 1
          )

plot2 = distribution_fcn_ls$rhyper %>% 
  sim_ylim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 10, n = 10, k = 10)",
          x_lim = c(-0.5, 10.5),
          y_lim1 = c(0,10000),
          y_lim2 = c(0,1),
          # distribution parameters ---
          m = 10, n = 10, k = 10
          )

plot3 = distribution_fcn_ls$rhyper %>% 
  sim_ylim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 10, n = 10, k = 20)",
          x_lim = c(-0.5, 10.5),
          y_lim1 = c(0,10000),
          y_lim2 = c(0,0.35),
          # distribution parameters ---
          m = 10, n = 10, k = 20
          )

plot1/plot2/plot3
```

2. changing m/n ratio

```{r}
plot1 = distribution_fcn_ls$rhyper %>% 
  sim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 2, n = 18, k = 10)",
          x_lim = c(-0.5, 10.5),
          # distribution parameters ---
          m = 2, n = 18, k = 10
          )

plot2 = distribution_fcn_ls$rhyper %>% 
  sim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 10, n = 10, k = 10)",
          x_lim = c(-0.5, 10.5),
          # distribution parameters ---
          m = 10, n = 10, k = 10
          )

plot3 = distribution_fcn_ls$rhyper %>% 
  sim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 18, n = 2, k = 10)",
          x_lim = c(-0.5, 10.5),
          # distribution parameters ---
          m = 18, n = 2, k = 10
          )

plot1/plot2/plot3
```

3. changing m, n, k magnitude

```{r}
plot1 = distribution_fcn_ls$rhyper %>% 
  sim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 10, n = 10, k = 10)",
          # x_lim = c(-0.5, 180.5),
          # distribution parameters ---
          m = 10, n = 10, k = 10
          )

plot2 = distribution_fcn_ls$rhyper %>% 
  sim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 100, n = 100, k = 100)",
          # x_lim = c(-0.5, 180.5),
          # distribution parameters ---
          m = 100, n = 100, k = 100
          )

plot3 = distribution_fcn_ls$rhyper %>% 
  sim_fcn(dist_name = distribution_name[9],
          bw = 0.01,
          plot_text = "rhyper(nn, m = 300, n = 300, k = 300)",
          # x_lim = c(-0.5, 180.5),
          # distribution parameters ---
          m = 300, n = 300, k = 300
          )

plot1/plot2/plot3
```


## `r paste(str_to_title(distribution_name[10]), "Distribution", paste0(distribution_fcn_name[10],"()"))`

```{r echo=TRUE}
args(distribution_fcn_ls$rlnorm)
```

meanlog, sdlog: mean and standard deviation of the distribution on the log scale with default values of 0 and 1 respectively.

```{r}
plot1 = distribution_fcn_ls$rlnorm %>% 
  sim_ylim_fcn(dist_name = distribution_name[10],
          bw = 0.2,
          plot_text = "rlnorm(n, meanlog = 0, sdlog = 1)",
          x_lim = c(-0.5, 15.5),
          y_lim1 = c(0,3000),
          y_lim2 = c(0,1),
          # distribution parameters ---
          meanlog = 0, sdlog = 1
          )

plot2 = distribution_fcn_ls$rlnorm %>% 
  sim_ylim_fcn(dist_name = distribution_name[10],
          bw = 0.2,
          plot_text = "rlnorm(n, meanlog = 1, sdlog = 1)",
          x_lim = c(-0.5, 15.5),
          y_lim1 = c(0,3000),
          y_lim2 = c(0,1),
          # distribution parameters ---
          meanlog = 1, sdlog = 1
          )

plot3 = distribution_fcn_ls$rlnorm %>% 
  sim_ylim_fcn(dist_name = distribution_name[10],
          bw = 0.2,
          plot_text = "rlnorm(n, meanlog = 1, sdlog = 0.5)",
          x_lim = c(-0.5, 15.5),
          y_lim1 = c(0,3000),
          y_lim2 = c(0,1),
          # distribution parameters ---
          meanlog = 1, sdlog = 5
          )

plot1/plot2/plot3
```









